---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README_",
  out.width = "100%"
)
```

# plotATLAS

<!-- badges: start -->
<!-- badges: end -->

The goal of plotATLAS is to plot data from various outputs produced from the ATLAS (Analysis Tools for Low-coverage and Ancient Samples) pipleline. 

## Installation

You can install the development version of plotJSON from [GitHub](https://github.com/pandeyaparna2022/plotATLAS) with:

``` r
# install.packages("devtools")
devtools::install_github("pandeyaparna2022/plotATLAS")
```

Alternatively you can also use the `pak` package:
```{r install_pak, eval = FALSE}
# install.packages("pak")
pak::pak("pandeyaparna2022/plotATLAS")
```

Or the `remotes` package:
```{r install_remotes, eval=FALSE}
# install.packages("remotes")
remotes::install_github("pandeyaparna2022/plotATLAS", build_vignettes = TRUE)
```

## Dependencies
- rjson
- ggplot2
- rlang
- stringr

## Usage

### Plot postmortem damage

```{r usage_PMD_}
library(plotATLAS)

# Assign path to the input file e.g path = "path/to/folder/ATLAS_data_RGInfo.json"

path <- list_example("test.json") #here the path is the internal test data provided with the package

# define readGroups if you wish to plot only certain readGroups
readGroups <- c("ERR8666961", "ERR8684188")

# define Side 5, 3 or both. Default is both.
side = 5

# plot PMD
plot_PMD(path, side, readGroups=readGroups)
plot_PMD(path, readGroups=readGroups)
plot_PMD(path)
```

### Plot Sequencing Error Covariates
```{r usage_covariates_}
library(plotATLAS)

# Assign path to the input file e.g path = "path/to/folder/ATLAS_data_RGInfo.json"
path <- list_example("test.json")
# define readGroups if you wish to plot only certain readGroups
readGroups <- c("ERR8666961", "ERR8684188")
#Plot covariates
Covariates = list('quality','position','context','fragmentLength','mappingQuality','rho')
for (i in Covariates){
plot_SeqError_covariate(path,i,1);

}
```
### Plot BAMDiagnostic Histograms
```{r, warnings=FALSE, usage_BAMDiagnostics_}
library(plotATLAS)
# Assign path to the directory with input files e.g path = "path/to/folder/Bamdiagnostic"
path <- list_example_folder()
plot_BAMdiagnostic(path, output_directory_name = getwd())


```


